Age-related changes in plant growth and traits

### 2016-12-01 scripts/RA_figs_201601129.Rmd
working through RA figs

>>>>

traits <- as.data.frame(select(SummarySpp[["mean"]],species,RA_leaf_area,RA_max_1,RA_vs_all_leaf,embryo_endo_costs,LMA,wood_density,growth_shoot_length,seed_count,lifespan,maturity,asymptotic_RA))
traits$maxH <- SummarySpp[["max"]]$height

temp <- subset(SummarySppAge[["mean"]], age >= asymptotic_RA)
temp <- temp %>%
        group_by(species) %>%
        summarise_each(funs(mean), RA_leaf_area,RA_max_1,RA_vs_all_leaf)
names(temp) <- c("species","RA_leaf_area_max","RA_max_1_max","RA_vs_all_leaf_max")

traits <- merge(traits,temp,by="species")

#win.metafile("figs2/RA/Figure_3_maxRA_correlates.wmf", height=11, width=8)
#plot
par(mfcol=c(3,2), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2))

i <- traits$RA_leaf_area_max
i <- traits$RA_max_1_max
i <- traits$RA_vs_all_leaf_max
for (i in c(traits$RA_leaf_area_max,traits$RA_max_1_max,traits$RA_vs_all_leaf_max)) {

plot(i~traits$lifespan,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("lifespan (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
# <- lm(log10(lifespan)~i,traits)
#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
mtext("maximum RA",2,outer=TRUE,line=1)

plot(i~traits$maturity,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("age at maturity (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
#mod <- lm(mature~log10(i),traits)
#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

plot(i~traits$embryo_endo_costs,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n",xlim=c(.005,30),xaxt="n")
mtext("embryo + endosperm weight (mg)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
axis(1, at=c(.01,.1,1,10), labels=c(.01,.1,1,10),las=1)
#mod <- lm(log10(embryo_endo_size)~i,traits)
#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")

plot(i~traits$maxH,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("maximum height (mm)",1,outer=FALSE,line=2)
#mod <- lm(log10(maxH)~i,traits)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

plot(i~traits$LMA,col=col.spp(traits$species),pch=16,cex=1.5,xlab="",yaxt="n",log="x")
mtext("LMA",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
#mod <- lm(LMA~RA_leaf_area,traits)
#extra.bottom.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

plot(i~wood_density,traits,col=col.spp(traits$species),pch=16,cex=1.5,xlab="",yaxt="n")
mtext("wood density",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
#mod <- lm(wood_density~i,traits)
#extra.top.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
#dev.off()
}

write.csv(traits, file="figs2/RA/Table01_maxRA_correlates.csv",row.names=FALSE)

plot(RA_per_year ~ i,traits,col=col.spp(species),pch=16,cex=2,log="y")
mod <- lm(i~log10(RA_per_year),traits)
summary(mod)

plot(seed_count ~ i,traits,col=col.spp(species),pch=16,cex=2,log="y")
